### 2024-03-13 thesis/input_files/point.tex
March 13th 2024

This chapter covers the theory of the most widely used method for point forecasting in the EF literature. Besides discussing the theory underlying these models, this chapter includes also a couple of worked examples in order to get acquainted with the practical applications of models.
\section{Exponential smoothing}

>>>>

This chapter covers the theory of the most widely used method for point forecasting in the EF literature. Besides discussing the theory underlying these models, this and the following chapter include also a couple of worked examples in order to get acquainted with the practical applications of models.
\section{Exponential smoothing}

### 2024-03-13 thesis/input_files/probabilistic.tex
March 13th 2024

\section{Quantile regression}
\input{input_files/qr.tex}

>>>>

When it comes to probabilistic forecasting, there are a couple of standard practical approaches; conceptually they can be grouped into two main categories. The former class of approaches tries modelling the distribution of the observed data directly. The latter family of approaches constructs first a point forecast and then learns the distribution of the model's errors.
\section{Quantile regression}
\input{input_files/qr.tex}
